Can We Crunch the Social Graph on the Cheap?

### 2011-01-25 doc/hotpar2011/softxmt-hotpar2011.tex
editing and refs up to eval

Note that we are not advocating using an FPGA as a memory controller
with attached DRAM and additional storage for full-empty bits. We
believe this unnecessarily complicates the design for such a
component. Our goal is to minimize the amount of hardware design our
proposal requires.

@@

We ran these experiments on a Dell PowerEdge R410 with two Xeon X5650 (Nehalem microarchitecture)
chips and 24GB of RAM, with hyperthreading disabled. These
chips use a NUMA memory architecture, where each chip has
its own integrated memory controller and DIMMs; references to other
chips' memory are carried over Intel's cache-coherent QuickPath
Interconnect (QPI).

>>>>

Note that we are not advocating using an FPGA as a memory controller
with attached DRAM and additional storage for full-empty bits. We
believe this unnecessarily complicates the design for such a
component. Our goal is to minimize the amount of hardware design our
proposal requires.
\todo{but are we eliminating the possibility of FE-only storage on the FPGA?}

@@

We ran these experiments on a Dell PowerEdge R410 with two Xeon X5650 (Nehalem microarchitecture)
chips and 24GB of RAM, with hyperthreading disabled. These
chips use a NUMA memory architecture, where each chip has
its own integrated memory controller and DIMMs; references to other
chips' memory are carried over Intel's cache-coherent QuickPath
Interconnect (QPI) \cite{quickpath:website}.
